Deriving Multi-Headed Planar Dependency Parses from Link Grammar Parses

### 2014-12-09 doc/slides/hong+eisner.TLT13.slides.tex
cleaned up the animations in the presentation

\subsection{Motivation}
\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for testing new parsing algorithms
    \item[]  
    \item[]  
    \item[]  
  \end{itemize}
}

\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for testing new parsing algorithms
    \item Such a corpus could be automatically annotated using Integer Linear Programming
    \item[]  
    \item[]  
  \end{itemize}
}

\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for testing new parsing algorithms
    \item Such a corpus could be automatically annotated using Integer Linear Programming
    \item We explored whether the Link Grammar could be adapted for this purpose.
    \item[]  
  \end{itemize}
}

\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for testing new parsing algorithms
    \item Such a corpus could be automatically annotated using Integer Linear Programming
    \item We explored whether the Link Grammar could be adapted for this purpose.
    \item The results of this are mixed, but provides a good case study.
  \end{itemize}
}

@@

\frame{\frametitle{ILP Results}
%  \begin{table}[h]
%    \begin{tabular}{|l|l||l|}
%      \hline
%      & & out of total \\ \hline
%      Link types & & \\allowing both directions & 7 & 113 \\ \hline
%      Link tokens & & \\requiring disallowed direction & & \\via slack & 4043 & 195,000 \\ \hline
%    \end{tabular}
%  \end{table}
  \begin{itemize}
  \item[] Link types that allowed both directions:
    \begin{itemize}
    \item[] 7 / 113 = 6.19\%
    \end{itemize}
  \item[] Link tokens that required disallowed direction via slack:
    \begin{itemize}
    \item[] 4043 / 195,000 = 2.07\%
    \end{itemize}
  \end{itemize}
  \begin{itemize}
  \item[]  
  \end{itemize}
}

\frame{\frametitle{ILP Results}
  \begin{itemize}
    \item[] Link types that allowed both directions:
      \begin{itemize}
      \item[] 7 / 113 = 6.19\%
      %\item[] $\frac{7}{113} = 6.19\%$ 
      \end{itemize}
    \item[] Link tokens that required disallowed direction via slack:
      \begin{itemize}
        %\item[] $\frac{4043}{195000} = 2.07\%$ 
        \item[] 4043 / 195,000 = 2.07\%
      \end{itemize}
  \end{itemize}
  \begin{itemize}
  \item[] The link labels mostly have a consistent direction.
  \end{itemize}
}

>>>>

\subsection{Motivation}
\frame{\frametitle{Motivation}
  \begin{itemize}
    \uncover<1->{\item A multiheaded dependency corpus would be useful for testing new parsing algorithms}
    \uncover<2->{\item Such a corpus could be automatically annotated using Integer Linear Programming}
    \uncover<3->{\item We explored whether the Link Grammar could be adapted for this purpose.}
    \uncover<4->{\item The results of this are mixed, but provides a good case study.}
  \end{itemize}
}

@@

\frame{\frametitle{ILP Results}
%  \begin{table}[h]
%    \begin{tabular}{|l|l||l|}
%      \hline
%      & & out of total \\ \hline
%      Link types & & \\allowing both directions & 7 & 113 \\ \hline
%      Link tokens & & \\requiring disallowed direction & & \\via slack & 4043 & 195,000 \\ \hline
%    \end{tabular}
%  \end{table}
  \begin{itemize}
    \item[] Link types that allowed both directions:
      \begin{itemize}
        \item[] 7 / 113 = 6.19\%
      \end{itemize}
    \item[] Link tokens that required disallowed direction via slack:
      \begin{itemize}
      \item[] 4043 / 195,000 = 2.07\%
      \end{itemize}
  \end{itemize}
  \begin{itemize}
    \uncover<1>{\item[]}
    \uncover<2->{\item[] The link labels mostly have a consistent direction.}
  \end{itemize}
}
